Supplementary Materials

### 2018-03-27 paper/appendix_modelDescription.tex
added model description in appendix

\usepackage{microtype}                 % use micro-typography (slightly more compact, better to read)
\PassOptionsToPackage{warn}{textcomp}  % to address font issues with \textrightarrow
\usepackage{textcomp}                  % use better special symbols
\usepackage{mathptmx}                  % use matching math font
\usepackage{times}                     % we use Times as the main font
\renewcommand*\ttdefault{txtt}         % a nicer typewriter font
\usepackage{cite}                      % needed to automatically sort the references
\usepackage{tabu}                      % only used for the table example
\usepackage{booktabs}                  % only used for the table example
%% We encourage the use of mathptmx for consistent usage of times font
%% throughout the proceedings. However, if you encounter conflicts
%% with other math-related packages, you may want to disable it.

@@

@@

\begin{document}
\firstsection{Appendix 1, Detailed description of the Model}
\maketitle

\section{Appendix 2, Code Example: Link Visualization with Model}
\begin{lstlisting}[language=Python, caption=Code for generating the visualization.]
from visPackage import *
from modelInterface import *
from sentenceGenerator import *

>>>>

\usepackage{microtype}                 % use micro-typography (slightly more compact, better to read)
\PassOptionsToPackage{warn}{textcomp}  % to address font issues with \textrightarrow
\usepackage{textcomp}                  % use better special symbols
\usepackage{mathptmx}                  % use matching math font
\usepackage{times}                     % we use Times as the main font
\renewcommand*\ttdefault{txtt}         % a nicer typewriter font
\usepackage{cite}                      % needed to automatically sort the references
\usepackage{tabu}                      % only used for the table example
\usepackage{booktabs}                  % only used for the table example
\usepackage{amsmath,bm}
%% We encourage the use of mathptmx for consistent usage of times font
%% throughout the proceedings. However, if you encounter conflicts
%% with other math-related packages, you may want to disable it.

@@

\newcommand{\taoli}[1]{\textcolor{orange}{[#1]}}

@@

\begin{document}
\firstsection{Appendix A: Detailed description of the Model}
\maketitle

The Decomposable Attention model is an end-to-end model that takes vectorized premise sentence and hypothesis sentence, and output a probability distribution over three labels. The pipeline can be separated into three phases: encoder, attention and classifier. Here we briefly formalize these three layers.

\subsection{Encoder}
Denote the premise sentence as $\overline{\boldsymbol{P}} = (\overline{\boldsymbol{p}}_1, \overline{\boldsymbol{p}}_2, ..., \overline{\boldsymbol{p}}_m)$ and hypothesis sentence as $\overline{\boldsymbol{H}} = (\overline{\boldsymbol{h}}_1, \overline{\boldsymbol{h}}_2, ..., \overline{\boldsymbol{h}}_n)$ where $\overline{\boldsymbol{p}}_i$ and $\overline{\boldsymbol{h}}_j$ are the input embedding vectors respectively. The purpose of encoder is to generate specialized encodings that will participate in the following steps of the model. Define the encoder function as
\begin{align}
  \boldsymbol{P} &= F(\overline{\boldsymbol{P}})\\
  \boldsymbol{H} &= F(\overline{\boldsymbol{H}})
\end{align}

where $F$ function is the encoder layer (e.g. a context-free two-layer ReLU). Let $\boldsymbol{P}$ denote the output premise encoding of size $m \times d$, and $\boldsymbol{H}$ the hypothesis encoding of size $n \times d$ where $d$ is the encoding size.

\subsection{Attention} \label{sec:att}
The job of attention layer is to capture pairwise interaction between encodings of premise and hypothesis. First we compute a similarity score matrix $\boldsymbol{S}$ ($m \times n$) by the following
\begin{align}
  S_{ij} &= \boldsymbol{p}_i ^T \boldsymbol{h}_j
\end{align}

Then attention weights are obtained by normalizing $\boldsymbol{S}$ bidirectionally. We will use $\leftarrow$ and $\rightarrow$ to differentiate the notation. That is, for premise token $\boldsymbol{p}_i$, a probability distribution over all $\boldsymbol{h}_j$`s are done as
\begin{align}
  \overleftarrow{\boldsymbol{a}}_i &= \frac{exp(S_{ij})}{\sum_{j \in h} exp(S_{ij})}
\end{align}

where $\overleftarrow{\boldsymbol{a}}_i$ is of dimension $1 \times n$ naturally. Similarly, for every $\boldsymbol{h}_j$, there is a probability distribution over all premise tokens.
\begin{align}
  \overrightarrow{\boldsymbol{a}}_j &= \frac{exp(S_{ij})}{\sum_{i \in p} exp(S_{ij})} \label{eq:aright}
\end{align}

where $\overrightarrow{\boldsymbol{a}}_j$ is a $1 \times m$ dimension. In case a token is not correlated with any other tokens, the model added an extra artificial token to both premise and hypothesis to allow a word aligning with null.

\subsection{Classifier} \label{sec:cls}
Classifier takes features from previous steps and predict a probability distribution over three labels. First, it aggregates features following the bidirectional attentions as
\begin{align}
  \boldsymbol{u}_i &= G([\overleftarrow{\boldsymbol{a}}_i \cdot \boldsymbol{H} \hspace{1ex} | \hspace{1ex}  \overline{\boldsymbol{p}}_i]) \\
  \boldsymbol{v}_j &= G([\overrightarrow{\boldsymbol{a}}_j \cdot \boldsymbol{P} \hspace{1ex}  | \hspace{1ex}  \overline{\boldsymbol{h}}_j])
\end{align}

where G is the aggregation layer (e.g. two-layer ReLU) and $[\cdot|\cdot]$ denotes concatenation. Notice this aggregation layer jointly considers embeddings, encodings and attentions. With the aggregated premise feature $\boldsymbol{u}_i$ and hypothesis feature $\boldsymbol{v}_j$, the classifier does further feature conjunction to predict weight on each entailment score:
\begin{align}
  \boldsymbol{y} &= Z([\sum_i \boldsymbol{u}_i | \sum_j \boldsymbol{v}_j]) \label{eq:yscore}
\end{align}

where $Z$ is another neural layer (e.g. two-layer ReLU followed by a linear layer). For training, the scores $\boldsymbol{y}$ are connected to multi-class cross entropy loss function. For inference, the predicted label is $\arg\max_i y_i$.

\taoli{Do we need citation in Appendix?}

\textbf{Comment} We used the same network setting in the Decomposable Attention paper (cite). That are, network hidden size is $200$; input word embeddings are $200$ embeddings (downsampled from $300$ dimensional GloVe embeddings (cite) by a learnable linear layer); dropout (cite) is $0.2$ for learning; and learning rate is $0.05$.

\section{Appendix B: Code Example: Link Visualization with Model}
\begin{lstlisting}[language=Python, caption=Code for generating the visualization.]
from visPackage import *
from modelInterface import *
from sentenceGenerator import *
